Malacology: A Programmable Storage System

### 2017-02-23 paper/7_future_work.tex
paper: integrate Carlos' future work comments
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\newcommentone{Some higher-level services that we plan to build using the
interfaces in Table~\ref{table:examples} are: an elastic cloud database, a data
processing engine, and a data layout manager.  The elastic database could use
the data I/O interface to push down predicates, the file type interface to
maintain access paths and statistics efficiently, and the durability interface
to manage ingestion and movement.  The data processing engine would be similar
to MapReduce, using the data I/O interface to send computation to the data, the
load balancing interface as a proxy for farming off work, and the durability
interface for persisting to input or output sinks.  Finally, the data layout
manager would be similar to DRepl~\cite{ionkov:msst2013}, using the file type,
durability, and data I/O interfaces to provide multiple views of data.}

>>>>

\newcommentone{Some higher-level services that we plan to build using the
interfaces in Table~\ref{table:examples} are: an elastic cloud database, a data
processing engine, and a data layout manager. Approaches proposed so far use
the data I/O interface to push down predicates and computation, the file type
interface to maintain access paths and metadata efficiently, and the durability
interface to manage ingestion and movement. Using the programmable storage
approach helps us build higher-level services that work well with the storage
system not in spite of it.}
